---
title: "Diamonds"
author: "Nasha Virata"
date: '2022-10-10'
output:
  pdf_document: default
  html_document: default
---

```{r knitr_opts, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  comment = "#>",
  collapse = TRUE
)
```

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)
```

```{r}
smaller <- diamonds %>%  
  filter(carat <= 2.5)
```

```{r}
comma <- function(x) 
  format(x, digits = 2, big.mark = ",")
```

We have data about `r nrow(diamonds)` diamonds. Only 
`r nrow(diamonds) - nrow(smaller)` are larger than
2.5 carats. The distribution of the remainder is shown
below:

```{r, echo = FALSE}
smaller %>%  
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

*Most* of the remaining diamonds are ^very^ ^small^, smaller than 0.5 carats although there are others clustered around the **1 carat** size 

## Exercise 27.4.7

### 1. Add a section that explores how diamond sizes vary by cut, colour, and clarity. Assume you’re writing a report for someone who doesn’t know R, and instead of setting echo = FALSE on each chunk, set a global option.

```{r}
colnames(diamonds)
```

### 2. Describe the largest 20 diamonds, including a table that displays their most recent attributes

The below plot shows us that diamonds that are lesser in quality tend to also be larger in size. 
```{r}
ggplot(diamonds, aes(y = carat, x = cut)) +
  geom_boxplot()
```

Similarly there is an inverse relationship between diamond color and size
```{r}
ggplot(diamonds, aes(y = carat, x = color)) +
  geom_boxplot()
```

And again, we see the trade off between size and the other characteristics with clarity and size
```{r}
ggplot(diamonds, aes(y = carat, x = clarity)) +
  geom_boxplot()
```

```{r results = "asis"}
largest <- diamonds %>% 
  arrange(desc(carat)) %>% 
  slice(1:20) %>% 
  select(carat, cut, color, clarity, depth) %>% 
  knitr::kable(
    caption = "The largest 20 diamonds in the `diamonds` dataset."
  )
```

### 3. Modify diamonds-sizes.Rmd to use comma() to produce nicely formatted output. Also include the percentage of diamonds that are larger than 2.5 carats.

```{r purl = FALSE}
large <- nrow(diamonds) - nrow(smaller)
percent_large <- large / nrow(diamonds) * 100
```

```{r}
percent_large
```

### 4. Set up a networks of chunks...

* we would use this setup for a new document*
##```{r setup, include = FALSE}
## knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
##```

The chunk 'a' has no dependencies
```{r a}
print(lubridate::now())
a <- 1
```
But the chunk 'b' depends on 'a'
```{r b, dependson = c("a")}
print(lubridate::now())
b <- a + 5
```
Chunk 'c' also depends on 'a'
```{r c, dependson = c("a")}
print(lubridate::now())
c <- a * 3
```
If I knit this document on a loop, the values from a, b, and c will be the same, because I cached them so will refer back to the original a, b, and c each time. 
